---
title: "Fire-Ants-Mtg01"
author: "Jason Battles"
date: "July 3, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## People
start with “who?” before we focus on “what?”.

## Mission
## Organization
- Benevolent Military Dictatorship.  
- We have to move forward efficiently.  Team consensus will guide our actions.  If consensus not achieved, then I decide….with love and benevolence in my heart.  ;-)
## Roles
like all special force units and task forces, you have been carefully selected for your skillsets (current and targeted for development).  I would like us to use a 2 man approach to tackling big items.  Based on what I think I know, I have some ideas on how we should group based on
## Decide on First Project
I will have 2 candidate projects for us to decide upon (MLB analysis, EMC Tech Refresh).  If you have a better idea for an app, be prepared to present it.  Again, consensus rules if you can state your case clearly and effectively.
## Next Steps
1. Code Repository
2. ChatOps
3. Task Tracking
4. Scrum / Sprint Schedule
5. Others?